Portfolio conservation of metapopulations\\under climate change

### 2014-01-08 inst/ms/salmonfolios.tex
Updates for prsb
A variety of changes prior to prsb submission

\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[round]{natbib}
\bibpunct{(}{)}{;}{a}{}{;}
\textheight 20.5cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\usepackage{booktabs}

@@

\widowpenalty=1000
\clubpenalty=1000

@@

\begin{document}
\raggedright

@@

\bibliographystyle{gcb}
\bibliography{jshort,ms}

@@

\section{Supporting information}

\textbf{Supporting code} Instructions for installing and using the \texttt{metafolio} \texttt{R} package.

\textbf{Table \ref{t:pars}}
Input parameters to the salmon metapopulation simulation with default values.

\textbf{Fig.\ \ref{f:stray}}
An example straying matrix.

\textbf{Fig.\ \ref{f:eg-sens}}
The impact of increasing or decreasing various parameter values on metapopulation return abundance.

\textbf{Fig.\ \ref{f:eg-sp-arma-full}}
Conserving a full range of response diversity (spatial conservation strategy) with short-term environmental fluctuations.

\textbf{Fig.\ \ref{f:eg-sp-arma-half}}
Conserving one half of response diversity (spatial conservation strategy) with short-term environmental fluctuations.

\textbf{Fig.\ \ref{f:ret-corr}}
A comparison of the log(returns) between populations.

\textbf{Fig.\ \ref{f:eg-sp-linear-full}}
Conserving a full range of response diversity (spatial conservation strategy) with long-term environmental change.

\textbf{Fig.\ \ref{f:eg-sp-linear-half}}
Conserving one half of response diversity (spatial
conservation strategy) with long-term environmental change.

\textbf{Fig.\ \ref{f:eg-n-arma-two}}
Two populations conserved with random response diversity and
short-term environmental fluctuations.

\textbf{Fig.\ \ref{f:eg-n-arma-sixteen}}
Sixteen populations conserved with random response diversity
and short-term environmental fluctuations.

\textbf{Fig.\ \ref{f:eg-n-linear-two}}
Two populations conserved with random response diversity and
long-term environmental change.

\textbf{Fig.\ \ref{f:eg-n-linear-sixteen}}
Sixteen populations conserved with random response diversity
and long-term environmental change.

>>>>

\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
%\usepackage[round]{natbib}
%\bibpunct{(}{)}{;}{a}{}{;}
\textheight 20.0cm
\usepackage{lineno}
\usepackage{xcolor}
\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\usepackage{booktabs}
\usepackage{cite}

@@

\widowpenalty=10000
\clubpenalty=10000

@@

\begin{document}
%\raggedright

@@

\bibliographystyle{prsb}
\bibliography{jshort,ms}

@@
